\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome} % social icons
\usepackage{geometry} % Margins
\input{glyphtounicode}
\pdfgentounicode=1

%----------FONT OPTIONS----------
% sans-serif
\usepackage[sfdefault]{FiraSans}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Set margins
\geometry{
  left=0.3in,
  right=0.3in,
  top=0.4in,
  bottom=0.3in
}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{
  \begin{itemize}[leftmargin=0.2in, label=\textbullet]
    \item\small{
      {#1 \vspace{-2pt}}
    }
  \end{itemize}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Josh Lin} \\ \vspace{1pt}
    \small \faPhone \thinspace \thinspace 647-891-5329
    $|$ \faEnvelope \thinspace \thinspace \href{mailto:joshlin.dev@gmail.com}{\underline{joshlin.dev@gmail.com}}
    $|$ \faLinkedin \thinspace \thinspace \href{https://linkedin.com/in/jiexulin}{\underline{linkedin.com/in/jiexulin}}
    $|$ \faGithub \thinspace \thinspace \href{https://github.com/linj121}{\underline{github.com/linj121}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {McMaster University}{Hamilton, ON}
      {Bachelor of Applied Science in Honours Computer Science}{September 2018 -- June 2023}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer}{July 2023 -- June 2024}
      {Longan Vision Corp.}{Hamilton, ON}
        \resumeItemListStart
          \resumeItem{Led a team of 3 in building a live stream platform from scratch, including designing, implementing, testing, and deploying the system using an agile approach, resulting in a scalable live streaming solution.}
          \resumeItem{In order to optimize video streaming latency, I researched and tested protocols including HLS, RTMP, RTSP, and WebRTC in a development environment. Successfully replaced the existing RTMP-HLS solution by choosing and integrating the protocol with the lowest latency (WebRTC), reduced latency from 6-8 seconds to under 1 second.}
          \resumeItem{Developed a dynamic video layout component using CSS Grid, allowing users to seamlessly toggle between multiple layouts and select cameras via a context menu, enhancing user experience and flexibility in monitoring video feeds.}
          \resumeItem{Tackled the scalability issue of P2P mesh network for WebRTC, researched and integrated a scalable video streaming architecture using a SFU (Selective Forwarding Unit) to transcode RTMP streams from IoT devices into WebRTC streams, optimizing uploading bandwidth and reducing load on client IoT devices.}
          \resumeItem{Set up and maintained the infrastructure on Google Cloud Compute Engine by using Docker Compose for container orchestration and Nginx as a reverse proxy, streamlined deployment process.}
        \resumeItemListEnd

    \resumeSubheading
      {Data Analyst Intern}{June 2021 -- January 2022}
      {Didi Global Inc.}{}
      \resumeItemListStart
        \resumeItem{Monitored daily market data by importing SQL query results into Excel reports and investigated anomalies by checking data sources and queries. Communicated business-related issues to supervisors and collaborated with the operations department for further investigation, summarizing insights in daily reports.}
        \resumeItem{Leveraged funnel analysis to examine data from both new and existing customers, identifying key areas of churn. Collaborated with the operations department to boost monthly customer retention rate by 5.2\%.}
        \resumeItem{Improved work efficiency and reduced manual work by automating daily SQL query and report generation utilizing Python integrated with chatbot API, which ensured timely report sharing to team members and stakeholders.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{\underline{\href{https://vizongroup.com}{Vizon}}} $|$ AI Recommendation Service for Computer Science Grad School Applicants}{May 2024 - Now}
        \resumeItemListStart
          \resumeItem{Developed an ETL process in Python to integrate diverse data sources of graduate school applicant data, creating a robust foundation for advanced analysis and machine learning model training.}
          \resumeItem{Designed and implemented RESTful APIs for authentication and user management, setting up Swagger UI documentation following OpenAPI standards, enhancing team collaboration and frontend-backend integration.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages}{: Python, SQL, TypeScript, Java, C++, CSS/HTML} \\
      \textbf{Others}{: Excel (Pivot Table, VLOOKUP, ...), Power Point} \\
     }}
 \end{itemize}

\end{document}
